Setting up Data

### 2020-05-31 src/SetupData.Rmd
realized total SC dataset missing some batches

```{r setup, include=FALSE}
library(plyr)
library(dplyr)
library(raster)#for cV
library(ggplot2)
library(knitr)
library(kableExtra)
library(here)
library(xlsx)
library(reshape2)
#knitr::opts_chunk$set(echo = FALSE)

@@

#total SC 
Total.SC_DF = read.xlsx2("~./MLH1repo/data/Total.SC_DF.xlsx", header=TRUE, 1)

Curated_BivData <-  read.csv("~./MLH1repo/data/Curated_BivData.csv", header=TRUE)

@@

@@

@@

#length( Curated_BivData %>% filter(hand.foci.count == "NA") )#36

table(Curated_BivData$hand.foci.count, exclude = NULL)
#there are ~600 rows with SC and no hand foci count (blah)
#Remove bivalent entries without hand foci count values
cleanCurated_BivData <-  Curated_BivData  %>%  filter(hand.foci.count  == 0 | hand.foci.count  == 1 |
                                      hand.foci.count  == 2 | hand.foci.count  == 3 | hand.foci.count  == 4 )

table(cleanCurated_BivData$hand.foci.count, exclude = NULL)

@@

                      n0CO = sum( (hand.foci.count == 0), na.rm = TRUE ),
                      n1CO = sum( (hand.foci.count == 1), na.rm = TRUE ),
                      n2CO = sum( (hand.foci.count == 2), na.rm = TRUE ),
                      n3CO = sum( (hand.foci.count == 3), na.rm = TRUE ),
                      n4CO = sum(hand.foci.count == 4, na.rm=TRUE),

                  proportion_0CO = (n0CO / nbiv),
                  proportion_1CO = (n1CO / nbiv),
                 proportion_2CO = (n2CO / nbiv),
                     proportion_3CO = (n3CO / nbiv),

@@

mouse.level.BivData_table$Rec.group <- ifelse(grepl("PWD male", mouse.level.BivData_table$category), 1, 
                              ifelse(grepl("MSM male", mouse.level.BivData_table$category), 1,
                                 ifelse(grepl("SKIVE male", mouse.level.BivData_table$category), 1, 0)))

@@

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_5.21.20.RData")

>>>>

```{r setup, include=FALSE}
library(plyr)
library(dplyr)
library(raster)#for cV
library(ggplot2)
library(knitr)
library(kableExtra)
library(here)
library(xlsx)
library(reshape2)

#knitr::opts_chunk$set(echo = FALSE)

@@

#total SC 
#new total_SC == will have all of the Batches

Total.SC_DF = read.xlsx2("~./MLH1repo/data/Total.SC_DF_5.31.20.xlsx", header=TRUE, 1) #this new total_SC has the additional batches and outliers have been removed

#Total.SC_DF = read.xlsx2("~./MLH1repo/data/Total.SC_DF.xlsx", header=TRUE, 1)

#original Curate_bivata + missing SKIVE female
Curated_BivData <-  read.csv2("~./MLH1repo/data/Curated_BivData_5.30.20.csv", sep=" ", header=TRUE)
#why they fuck was this space deliminated? I hate excel uggg

@@

```{r missing.curated.data, echo=FALSE, include=FALSE, eval=FALSE}

#Curated.missing.SKIVE.female = read.xlsx2("Curated_missing.SKIVE.female.xlsx", header=TRUE, 1)
Curated.missing.SKIVE.female$Foci4 <- ''
Curated.missing.SKIVE.female$PER_Foci_4 <- ''

Curated.missing.SKIVE.female$dis.cent <- ''
Curated.missing.SKIVE.female$dis.cent.PER <- ''

Curated_BivData_new.skive <- rbind(Curated_BivData, Curated.missing.SKIVE.female)

#write.xlsx2(Curated_BivData_new.skive, "Curated_BivData_5.30.20.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)

@@

```{r remove.non.foci, echo=FALSE}
#length( Curated_BivData %>% filter(hand.foci.count == "NA") )#36
str(Curated_BivData)
table(Curated_BivData$hand.foci.count, exclude = NULL)
#there are ~600 rows with SC and no hand foci count
table( (Curated_BivData %>% filter(  is.na(hand.foci.count) ) )$category )
#KAZ male and WSB female have >100 observations without hand.foci.counts

#Remove bivalent entries without hand foci count values
cleanCurated_BivData <-  Curated_BivData  %>%  filter(hand.foci.count  == 0 | hand.foci.count  == 1 |
                                      hand.foci.count  == 2 | hand.foci.count  == 3 | hand.foci.count  == 4 )

table(cleanCurated_BivData$hand.foci.count, exclude = NULL)
#600 removed
```

```{r format.str.Curate_BivData, echo=FALSE}
#new.Curate.FULL to Curated_BivData

#missing.SKIVE.female

#missing.SKIVE.female=read.xlsx2("~./MLH1repo/data/missing_SKIVE_female.xlsx", header=TRUE, 1)

#
Curated_BivData <- Curated_BivData[!(is.na(Curated_BivData$fileName) | Curated_BivData$fileName==""), ]
#this takes a while to run

#new.Curate.FULL <- add_mouse(new.Curate.FULL)#this function is v.slow for this big file
#new.Curate.FULL.org$Obj.ID <- paste(new.Curate.FULL.org$fileName, new.Curate.FULL.org$boxNumber, sep = "_")

#SC PASS
Curated_BivData <- Curated_BivData[Curated_BivData$SC.pass == '1',]#
#10480 #9819, #9769

#fix these duplicated ones
#check duplicates
#anyDuplicated(missing.SKIVE.female$Obj.ID)
#0 duplicates for missing SKIVE.f
#remove duplicates
Curated_BivData <- Curated_BivData %>% distinct()#from 8933 to 8151

Curated_BivData <- add_mouse(Curated_BivData)
Curated_BivData <- add_category(Curated_BivData)
Curated_BivData <- add_strain(Curated_BivData)
Curated_BivData <- add_sex(Curated_BivData)
Curated_BivData <- add_subsp(Curated_BivData)
Curated_BivData <- add_species(Curated_BivData)

#don't think I need this one
#Foci_TRUE_Curate_BivData <-   Curated_BivData[(!is.na(Curated_BivData$hand.foci.count)),]

##change factor cols to numbers (factor -> chr -> number)
Curated_BivData$fileName <- as.character(Curated_BivData$fileName)
Curated_BivData$Obj.ID <- as.character(Curated_BivData$Obj.ID)

Curated_BivData$centromere_ABS_Position <- as.character(Curated_BivData$centromere_ABS_Position)
Curated_BivData$centromere_PER_Position <- as.character(Curated_BivData$centromere_PER_Position)
Curated_BivData$chromosomeLength <- as.character(Curated_BivData$chromosomeLength)

Curated_BivData$hand.foci.count <- as.character(Curated_BivData$hand.foci.count)

Curated_BivData$Foci1 <- as.character(Curated_BivData$Foci1)
Curated_BivData$Foci2 <- as.character(Curated_BivData$Foci2)
Curated_BivData$Foci3 <- as.character(Curated_BivData$Foci3)
Curated_BivData$Foci4 <- as.character(Curated_BivData$Foci4)

##Numeric
Curated_BivData$centromere_ABS_Position <- as.numeric(Curated_BivData$centromere_ABS_Position)
Curated_BivData$centromere_PER_Position <- as.numeric(Curated_BivData$centromere_PER_Position)
Curated_BivData$chromosomeLength <- as.numeric(Curated_BivData$chromosomeLength)

Curated_BivData$hand.foci.count <- as.numeric(Curated_BivData$hand.foci.count)

Curated_BivData$Foci1 <- as.numeric(Curated_BivData$Foci1)
Curated_BivData$Foci2 <- as.numeric(Curated_BivData$Foci2)
Curated_BivData$Foci3 <- as.numeric(Curated_BivData$Foci3)
Curated_BivData$Foci4 <- as.numeric(Curated_BivData$Foci4)
#I think the number of sig figs and rounding changes slightly from the blocks above

#adding more feature calculations (IFD, ect)
Curated_BivData <- add_IFD(Curated_BivData)#fixed a bug
Curated_BivData$IFD1_PER = Curated_BivData$IFD1_ABS / Curated_BivData$chromosomeLength

#IFD functions
#  - IFD: currently I think just does 2CO bivalents 
#  - IFD.2: for mulitple IFDs (3CO ect.)

#IFD.2 does mulitple IFDs (just absolute)
#Curated_BivData <- add_IFD.2(Curated_BivData)

Curated_BivData$PER_Foci_1 <- Curated_BivData$Foci1 / Curated_BivData$chromosomeLength
Curated_BivData$PER_Foci_2 <- Curated_BivData$Foci2 / Curated_BivData$chromosomeLength
Curated_BivData$PER_Foci_3 <- Curated_BivData$Foci3 / Curated_BivData$chromosomeLength
Curated_BivData$PER_Foci_4 <- Curated_BivData$Foci4 / Curated_BivData$chromosomeLength

Curated_BivData$PER_Foci_1 <- as.numeric(Curated_BivData$PER_Foci_1)
Curated_BivData$PER_Foci_2 <- as.numeric(Curated_BivData$PER_Foci_2)
Curated_BivData$PER_Foci_3 <- as.numeric(Curated_BivData$PER_Foci_3)
Curated_BivData$PER_Foci_4 <- as.numeric(Curated_BivData$PER_Foci_4)

#not working
Curated_BivData$dis.cent <- Curated_BivData$Foci1 - Curated_BivData$centromere_ABS_Position
Curated_BivData$dis.cent.PER  <- Curated_BivData$dis.cent / Curated_BivData$chromosomeLength

#add telomere.dist
Curated_BivData$telo_dist <- ifelse(grepl(1, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength - Curated_BivData$Foci1), 
                     ifelse(grepl(2, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength -  Curated_BivData$Foci2), 
                     ifelse(grepl(3, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength - Curated_BivData$Foci3),
                    ifelse(grepl(4, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength - Curated_BivData$Foci4),   0))) )

Curated_BivData$telo_dist_PER <- Curated_BivData$telo_dist / Curated_BivData$chromosomeLength

#sis.co.ten
Curated_BivData <- add_SisCoTen(Curated_BivData)

#add rec.group
#divide musc males into groups
Curated_BivData$Rec.group <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
                                  ifelse(grepl("MSM male", Curated_BivData$category), 1,
                                  ifelse(grepl("SKIVE male", Curated_BivData$category), 1,
                                           0)))

#remove bivalent entries without hand foci count values
cleanCurated_BivData <-  Curated_BivData  %>%  filter(hand.foci.count  == 0 | hand.foci.count  == 1 |
                                      hand.foci.count  == 2 | hand.foci.count  == 3 | hand.foci.count  == 4 )

#write excel file
#write.xlsx2(missing.SKIVE.female, "Curated_missing.SKIVE.female.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)

@@

@@

                      n0CO = sum( (hand.foci.count == 0), na.rm = TRUE ),
                      n1CO = sum( (hand.foci.count == 1), na.rm = TRUE ),
                      n2CO = sum( (hand.foci.count == 2), na.rm = TRUE ),
                      n3CO = sum( (hand.foci.count == 3), na.rm = TRUE ),
                      n4CO = sum( (hand.foci.count == 4), na.rm=TRUE),

                  proportion_0CO = (n0CO / nbiv),
                  proportion_1CO = (n1CO / nbiv),
                 proportion_2CO = (n2CO / nbiv),
                     proportion_3CO = (n3CO / nbiv),
                 proportion_4CO = (n4CO / nbiv),

@@

mouse.level.BivData_table$Rec.group <- ifelse(grepl("PWD male", mouse.level.BivData_table$category), 1, 
                              ifelse(grepl("MSM male", mouse.level.BivData_table$category), 1,
                                 ifelse(grepl("SKIVE male", mouse.level.BivData_table$category), 1, 0)))
```

@@

#look at date of imaging affects on total SC
#count=1
#for(i in MLH1_data$Original.Name){
   # print(i)
#    templist= strsplit(i, split="_")[[1]]
#    c = (templist[1])
#    MLH1_data$image.string[count] <-  c
    #mini$image.date[count] <-  as.Date(c, format='%d%b%y')  #"%d%b%y")
#    count= count +1
#}
#works better if dat is converted out of image
#MLH1_data$date.imaged <- as.Date(MLH1_data$image.string,  format='%d%b%y')

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_5.30.20.RData")
